seqwish: very large variation graph inducer

### 2021-11-20 manuscript/main.tex
notes

    \section{Implementation}
    \label{sec:implementation}
    As input, we have $Q$, which is a concatenation of the sequences from which we will build the graph.
    We build a compressed suffix array (CSA) mapping sequence names to offsets in $Q$, and also the inverse using a rank/select dictionary on a bitvector marking the starts of sequences in $Q$.
    This allows us to map between positions in the sequences of $Q$, which is the format in which alignment algorithms typically express alignments, and positions in $Q$ itself, which is the coordinate space we will use as a basis for the generation of our graph.
    We encode the set of input pairwise alignments between sequences in $Q$ as object $A$.
    Although these alignments tend to be represented using oriented interval pairs in $Q$, for simplicity and robustness to graph complexity, we describe $A$ as a set of pairs of bidirectional positions (sequence offsets and strands) $[1 \ldots |Q_1 \ldots Q_{|Q|}|]$ , such that $A = \{ (b_{q}, b_{r}), \ldots \}$.
    We sort $A$ by the first member ($b_{q}$) of each pair, ensuring that the entries in $A$ are ordered according to their order in $Q$.

@@

>>>>

    \section{Implementation}
    \label{sec:implementation}

    \FIXME{The algorithm validates some aspects of itself, we should point that out}

    As input, we have $Q$, which is a concatenation of the sequences from which we will build the graph.
    We build a compressed suffix array (CSA) mapping sequence names to offsets in $Q$, and also the inverse using a rank/select dictionary on a bitvector marking the starts of sequences in $Q$.
    This allows us to map between positions in the sequences of $Q$, which is the format in which alignment algorithms typically express alignments, and positions in $Q$ itself, which is the coordinate space we will use as a basis for the generation of our graph.
    We encode the set of input pairwise alignments between sequences in $Q$ as object $A$.
    Although these alignments tend to be represented using oriented interval pairs in $Q$, for simplicity and robustness to graph complexity, we describe $A$ as a set of pairs of bidirectional positions (sequence offsets and strands) $[1 \ldots |Q_1 \ldots Q_{|Q|}|]$ , such that $A = \{ (b_{q}, b_{r}), \ldots \}$.
    We sort $A$ by the first member ($b_{q}$) of each pair, ensuring that the entries in $A$ are ordered according to their order in $Q$.

@@

    %The alignment is taken as truth, so some of the cross validation things we do for pggb are irrelevant.
    %The one experiment could be graph induction on many graphs, with a 2D/3D plot with input size (alignments) vs induction time and color/shape to show graph output size or something
    %Or
    %We go schematic with the figure to show a complex but very detailed example with the algorithm worked out
